\LaTeX\ Author Guidelines for ICCV Proceedings

### 2020-03-10 chapters/supplementary.tex
Update supplementary

\begin{figure*}
        \centering
\begin{minipage}{0.49\textwidth}
\centering
        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
    \end{minipage} \hfill
\begin{minipage}[T]{0.48\textwidth}
    \centering
    \small
                \begin{tabular}[b]{r | l }
            \toprule
            Linkage criteria & Update rule $f$ \\        
            \midrule
            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} \\ 
            \makecell[r]{Absolute \\Maximum:} & \thead[l]{
            $
            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
            $}
               \\ 
            \makecell[r]{Average:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                 \\ 
            Maximum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} \\
            Minimum:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} 
        \end{tabular}
\end{minipage}
\caption{ 
\textbf{Left:} Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction. \textbf{Right:} The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.}
\label{fig:edge_contraction_and_contr_graph}  
\end{figure*}

@@

\paragraph*{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed, as shown in Algorithm \ref{main_alg}.  
An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph. Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that there exists exactly one representative $|\tilde{V} \cap S| = 1$ for every cluster $S \in \Pi$ . Edges in $\tilde{E}$ represent adjacency-relationships between clusters 
and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 
For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$. Thus, we can recompute these interactions by using an \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$:
\begin{align}
  \interact(S_u \cup S_v,S_t) =& f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] \\
  =& f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
\end{align}
In Fig. \ref{fig:edge_contraction_and_contr_graph} we show an example of edge contraction and we list the update rules associated to the linkage criteria we introduced in Table \ref{tab:linkage-criteria}.

@@

\paragraph*{Complexity} In the main loop, the algorithm iterates over all edges, but the only iterations presenting a complexity different from $\mathcal{O}(1)$ are the ones involving a merge of two clusters, which are at most $N-1$. By using a union-find data structure (with path compression and union by rank) the time complexity of \texttt{merge}$(u, v)$ and \texttt{find}($u$) operations is $\mathcal{O}(\alpha(N))$, where $\alpha$ is the slowly growing inverse Ackerman function. The algorithm then iterates over the neighbors of the merged cluster (at most $N$) and updates/deletes values in the priority queue ($\mathcal{O}(\log |E|)$). Therefore, similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$. In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory. Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$. 
With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$. 
Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity. %\TODO{Empirical complexity plot?}

\begin{algorithm*}
  \caption{Mutex Watershed Algorithm proposed by \cite{wolf2018mutex}}
\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges \\
\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State \texttt{UF} $\gets$ initUnionFind($V$) 
      \For{$(u,v)=e\in E$ in descending order of $|w_e|=|w_e^+ - w_e^-|$}
        \If{\texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$)} \Comment{Check if $u,v$ are already in the same cluster}
          \If{({\color{ForestGreen}\textbf{$w_e > 0$}}) \textbf{and} \texttt{canBeMerged}($u,v$)}  \Comment{Check for cannot-link constraints}
            \State \texttt{UF}.merge($u,v$) and inherit constraints of parent clusters
          \ElsIf{({\color{red}\textbf{$w_e \leq 0$}})}
            \State Add cannot-link constraints between parent clusters of $u,v$
          \EndIf
        \EndIf
      \EndFor
      \State
      \Return Final clustering given by union-find data structure \texttt{UF}
  \end{algorithmic}
  \label{alg:mutex_watershed}
\end{algorithm*}

@@

\begin{prop} \label{prop:equiv_MWS}
The Mutex Watershed Algorithm \ref{alg:mutex_watershed} (MWS) with empirical $\mathcal{O}(N \log N)$ complexity introduced by \cite{wolf2018mutex} returns the same final clustering given by the \algname{} Algorithm \ref{detailed_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
\begin{equation}\label{eq:def_abs_max}
f_{\mathrm{Abs.Max.}}(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
\end{equation}
\end{prop}
\begin{proof}
Both algorithms sort edges in descending order of the absolute interactions $|w_e|$ and then iterate over all of them. The only difference is that MWS, after merging two clusters, does not update the interactions between the new cluster and its neighbors. 
However, since with an Abs. Max. linkage the interaction between clusters is simply given by the edge with highest absolute weight $|w_e|$, the order by which edges are iterated over in \algname{} is never updated. Thus, both algorithms perform precisely the same steps and return the same clustering.
\end{proof}
\begin{prop} \label{prop:abs_max_cannot_link_property}
The \algname{} Algorithm \ref{detailed_alg} with the Absolute Maximum linkage defined in Eq. \ref{eq:def_abs_max} returns the same final clustering whether or not cannot-link constraints are enforced. 
\end{prop}
\begin{proof}
In the \algname{} Algorithm \ref{detailed_alg}, the clustering is updated only when two clusters are merged and the condition at line 9 is satisfied. 
We also observe that, in the unconstrained version of \algname{}, the predicate \texttt{canBeMerged} at line 9 can never be false because cannot-link constraints are never introduced at line 14.
Let us now contradict the initial hypothesis and assume by absurd that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version. 
This can happen only in the situation shown in Fig. \ref{fig:abs_max_proof_example}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$. 
Then, according to Eq. \ref{eq:def_abs_max}, the new merged cluster $uv$ and $t$ are constrained and share a positive interaction. 
But this case can never happen, since if $|w_{vt}|>|w_{ut}|$ then clusters $v$ and $t$ are merged before clusters $u$ and $t$ are constrained.  
\end{proof}

\begin{figure*}
        \centering

        \includegraphics[width=0.7\textwidth]{./figs/proof_abs_max_example.pdf} % left bottom right top
\caption{\algname{} with \emph{AbsMax} linkage: Example representing the only case of edge contraction $e_{uv}$ that would introduce a positive attractive interaction between two constrained clusters. Note this can actually never happen with an \emph{AbsMax} linkage, because edge $e_{ut}$ has a lower absolute priority as compared to $e_{uv}$, so clusters $u$ and $t$ cannot have been constrained before $u$ and $v$ are merged.
}
\label{fig:abs_max_proof_example}  
\end{figure*}

@@

\begin{table*}[t]
\centering
    \footnotesize
        \begin{tabular}{l|c|c|c|c|c}
          \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
        \end{tabular}
        \vspace*{1.1em}
    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
    CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
    CLC stands for cannot-link constraints. For all algorithms, the chosen value of bias parameter was $\beta = 0$. We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments.}
    \label{tab:extended_results_cremi}
\end{table*}

@@

The experiments summarized in Fig. \ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria. For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
\begin{figure*}[t]
\centering
\begin{minipage}[T]{0.61\textwidth}
\centering
        \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
    \captionof{figure}{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise. (\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Under-clustering biased version $\tilde{F}_{+}(x;\mathcal{K})$ of the predictions defined in Eq. \ref{eq:noise_biased_predictions} with $\mathcal{K}=8$ (\textbf{d}) Over-clustering biased version $\tilde{F}_{-}(x;\mathcal{K})$. Long-range predictions are not shown.
    }
    \label{fig:noisy_affs}
\end{minipage}\hfill
\begin{minipage}[T]{0.35\textwidth}
    \centering
    \small
    \vspace*{1.6em}
        \begin{tabular}{l|c|c}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \vspace*{0.5em}
    \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster. CLC stands for cannot-link constraints}
    \label{tab:extended_results_cityscapes_val}
\end{minipage}
\end{figure*}

>>>>

@@

\paragraph*{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed, as shown in Algorithm \ref{main_alg}.  
An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph. Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that there exists exactly one representative $|\tilde{V} \cap S| = 1$ for every cluster $S \in \Pi$ . Edges in $\tilde{E}$ represent adjacency-relationships between clusters 
and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 
For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$. Thus, we can recompute these interactions by using an \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$:
\begin{align}
  \interact(S_u \cup S_v,S_t) =& f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] \\
  =& f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
\end{align}
In Fig. \ref{fig:edge_contraction_and_contr_graph} we show an example of edge contraction and in Table \ref{tab:linkage_criteria_explicit} we list the update rules associated to the linkage criteria we introduced in Table \ref{tab:linkage-criteria}.

@@

\paragraph*{Complexity} In the main loop, the algorithm iterates over all edges, but the only iterations presenting a complexity different from $\mathcal{O}(1)$ are the ones involving a merge of two clusters, which are at most $N-1$. By using a union-find data structure (with path compression and union by rank) the time complexity of \texttt{merge}$(u, v)$ and \texttt{find}($u$) operations is $\mathcal{O}(\alpha(N))$, where $\alpha$ is the slowly growing inverse Ackerman function. The algorithm then iterates over the neighbors of the merged cluster (at most $N$) and updates/deletes values in the priority queue ($\mathcal{O}(\log |E|)$). 
Therefore, similarly to a heap-based implementation of hierarchical agglomerative clustering, our implementation of \algname{} has a complexity of $\mathcal{O}(N^2 \log N)$. In the worst case, when the graph is dense and $|E|=N^2$, the algorithm requires $\mathcal{O}(N^2)$ memory. Nevertheless, in our practical applications the graph is much sparser, so $\mathcal{O}(|E|)=\mathcal{O}(N)$. 
With a single-linkage, corresponding to the choice of the \emph{Maximum} update rule in our framework, the algorithm can be clearly implemented by using the more efficient Kruskal's Minimum Spanning Tree algorithm with complexity $\mathcal{O}(N \log N)$. 
Moreover, in the next section, we present an efficient implementation of \algname{} with \emph{Absolute Maximum} linkage that has empirical $\mathcal{O}(N \log N)$ complexity. %\TODO{Empirical complexity plot?}
\begin{figure}[H]
        \centering
        \includegraphics[width=0.6\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
    \centering
    \caption{Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction.}\label{fig:edge_contraction_and_contr_graph}  
\end{figure}
\begin{table}[H]
\centering
    \small
    \vspace{-2em}
\begin{tabular}[t]{r | l }
            \toprule
            Linkage criteria & Update rule $f$ \\        
            \midrule
            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} \\ 
            \makecell[r]{Absolute \\Maximum:} & \thead[l]{
            $
            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
            $}
               \\ 
            \makecell[r]{Average:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                 \\ 
            Maximum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} \\
            Minimum:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} 
        \end{tabular}\vspace{1em}
        \caption{The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.}
\label{tab:linkage_criteria_explicit}  
\end{table}

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.7\textwidth]{./figs/proof_abs_max_example.pdf} % left bottom right top
\caption{\algname{} with \emph{AbsMax} linkage: Example representing the only case of edge contraction $e_{uv}$ that would introduce a positive attractive interaction between two constrained clusters. Note this can actually never happen with an \emph{AbsMax} linkage, because edge $e_{ut}$ has a lower absolute priority as compared to $e_{uv}$, so clusters $u$ and $t$ cannot have been constrained before $u$ and $v$ are merged.
}
\label{fig:abs_max_proof_example}  
\end{figure*}
\begin{algorithm*}[t]
  \caption{Mutex Watershed Algorithm proposed by \cite{wolf2018mutex}}
\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges \\
\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State \texttt{UF} $\gets$ initUnionFind($V$) 
      \For{$(u,v)=e\in E$ in descending order of $|w_e|=|w_e^+ - w_e^-|$}
        \If{\texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$)} \Comment{Check if $u,v$ are already in the same cluster}
          \If{({\color{ForestGreen}\textbf{$w_e > 0$}}) \textbf{and} \texttt{canBeMerged}($u,v$)}  \Comment{Check for cannot-link constraints}
            \State \texttt{UF}.merge($u,v$) and inherit constraints of parent clusters
          \ElsIf{({\color{red}\textbf{$w_e \leq 0$}})}
            \State Add cannot-link constraints between parent clusters of $u,v$
          \EndIf
        \EndIf
      \EndFor
      \State
      \Return Final clustering given by union-find data structure \texttt{UF}
  \end{algorithmic}
  \label{alg:mutex_watershed}
\end{algorithm*}

@@

\begin{prop} \label{prop:equiv_MWS}
The Mutex Watershed Algorithm \ref{alg:mutex_watershed} (MWS) with empirical \linebreak $\mathcal{O}(N \log N)$ complexity introduced by \cite{wolf2018mutex} returns the same final clustering given by the \algname{} Algorithm \ref{detailed_alg} with the use of cannot-link constraints and an Absolute Maximum update rule:
\begin{equation}\label{eq:def_abs_max}
f_{\mathrm{Abs.Max.}}(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
\end{equation}
\end{prop}
\begin{proof}
Both algorithms sort edges in descending order of the absolute interactions $|w_e|$ and then iterate over all of them. The only difference is that MWS, after merging two clusters, does not update the interactions between the new cluster and its neighbors. 
However, since with an Abs. Max. linkage the interaction between clusters is simply given by the edge with highest absolute weight $|w_e|$, the order by which edges are iterated over in \algname{} is never updated. Thus, both algorithms perform precisely the same steps and return the same clustering.
\end{proof}
\begin{prop} \label{prop:abs_max_cannot_link_property}
The \algname{} Algorithm \ref{detailed_alg} with the Absolute Maximum linkage defined in Eq. \ref{eq:def_abs_max} returns the same final clustering whether or not cannot-link constraints are enforced. 
\end{prop}
\begin{proof}
In the \algname{} Algorithm \ref{detailed_alg}, the clustering is updated only when two clusters are merged and the condition at line 9 is satisfied. 
We also observe that, in the unconstrained version of \algname{}, the predicate \texttt{canBeMerged} at line 9 can never be false because cannot-link constraints are never introduced at line 14.
Let us now contradict the initial hypothesis and assume by absurd that the constrained version of \algname{} introduces a cannot-link constraints between two clusters sharing a positive interaction $\tilde{w}>0$ and outputs a different clustering as compared to the unconstrained version. 
This can happen only in the situation shown in Fig. \ref{fig:abs_max_proof_example}, when two clusters $u$ and $v$ are merged together and share a common neighboring node $t$ having the following two properties: a) $u$ and $t$ are already constrained and share a repulsive interaction $w_{ut}\leq0$, b) $v$ and $t$ share an attractive interaction $w_{vt}>0$ that is higher in absolute value $|w_{vt}|>|w_{ut}|$. 
Then, according to Eq. \ref{eq:def_abs_max}, the new merged cluster $uv$ and $t$ are constrained and share a positive interaction. 
But this case can never happen, since if $|w_{vt}|>|w_{ut}|$ then clusters $v$ and $t$ are merged before clusters $u$ and $t$ are constrained.  
\end{proof}

@@

\begin{table*}[t]
\centering
    \scriptsize
        \begin{tabular}{l|c|c|c|c|c}
          \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
        \end{tabular}
        \vspace*{1.1em}
    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
    CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
    CLC stands for cannot-link constraints. For all algorithms, the chosen value of bias parameter was $\beta = 0$. We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments.}
    \label{tab:extended_results_cremi}
\end{table*}

@@

The experiments summarized in Fig. \ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria. For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
\begin{figure}[t]
\centering
        \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
    \caption{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise. (\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Under-clustering biased version $\tilde{F}_{+}(x;\mathcal{K})$ of the predictions defined in Eq. \ref{eq:noise_biased_predictions} with $\mathcal{K}=8$ (\textbf{d}) Over-clustering biased version $\tilde{F}_{-}(x;\mathcal{K})$. Long-range predictions are not shown.
    }
    \label{fig:noisy_affs}
\end{figure}
\begin{table}
    \centering
    % \small
    \vspace*{0.6em}
        \begin{tabular}{l|c|c}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \vspace*{2em}
    \caption{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster. CLC stands for cannot-link constraints}
    \label{tab:extended_results_cityscapes_val}
\end{table}
